Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.

### 2012-08-12 article.tex
Hai

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
The estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance, hence lower MSE, indicating better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
Also, due to the stochastic nature of SAR processing, hence, of the underlying simulation process, 
	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of this statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not applicable,
	as alternative evaluation criteria are proposed.
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

The common theme is that each newly proposed speckle filter tends to be published along with a customised methodology for evaluating its own performance.
Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, regretably it lacks scientific objectivity. 
Some papers do present quantitative measurements, 
	however  due to the lack of a standardized performance criteria, 
	the evaluation metrics can change eccentrically from one paper to the next.

In this paper, we propose the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The rest of this paper is structured as follows.
While Section \ref{sec:lit_review} briefly surveys related work in published literature, Section \ref{sec:log_transform} provides a quick discussion of the Logarithmic Transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
	to choose the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, section \ref{sec:discussion} discusses the findings and presents concluding remarks.

@@

%Addressing this issue, 
%There have been a few published articles dedicated to the topic of evaluating speckle filters.
%However, our survey of SAR speckle filtering research indicates 
%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
%In this section, we briefly review published work 
%	related to the topic of evaluating SAR speckle filters.	
It is customary to divide the evaluation of speckle filters into two scenarios:
	homogeneous areas and heterogeneous scenes.
In homogeneous areas,
	speckle filters are expected to estimate with negligible radiometric bias.
Thus evaluating speckle filters on homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
By contrast, the methodologies used to evaluate speckle filters in heterogeneous areas are much more complex, probably due to the following difficulties.
The first difficulty is to find out an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is to come up with a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
In this section, various published work in evaluating SAR speckle filters are reviewed.

The metric to evaluate speckle filter should be relevant to the normal usage of such filters.
The general requirement for a speckle filter in SAR processing frameworks is that its application should allow easier measurement, detection and classification of the underlying radiometric features.
%As shown in the subsequent section, 
%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirement of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

For homogeneous scenes, 
	where the underlying radiometry is assumed to be constant, 
	the filtered results, statistically speaking, are considered to be samples of 
		a single but complex stochastic process.
%Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
Then, from the logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
	%are expected to estimate with no radiometry bias. 
%The best filters achieve maximum speckle suppression power in such areas.

A metric that can be used to detect radiometric distortion is the ratio between the estimated number and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent index for evaluation would, of course, be a simple substraction.
In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.

@@

A few metrics have been used to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the log-transformed domain.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters which is the primary criteria to evaluate speckle filters over homogeneous area.
%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
%	which is a component of MSE evaluation, 
%	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.

Real-life and practical images, however, are not homogeneous.
Thus there are a few associated difficulties in evaluating speckle filters in heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
It is trivially easy to estimate the underlying radiometric co-efficient if an area is known to be homogeneous
However, without simulation or access to lab environment ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters' estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise the noise being removed, (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluation, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
The ratio image then becomes a simple substraction image.
The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).

@@

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional level.
In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

@@

Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
However since SAR data is heteroskedastic, which violaes the assumptions of Gauss Markov theorem, the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. 
Others have suggest the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

@@

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss Markov theorem becomes applicable again, 
	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
Initial intitution suggests that each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is presented, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

@@

SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scaterring components, each reflecting from different and distributed elementary scaterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. These interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.

@@

It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
These relationships evidently manifest a mutiplicative nature. 
In fact, this condition has long been noted, but from different perspectives, in various SAR models including multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. Consequently, the population expected mean and variance of the four distributions are given in table \ref{tbl:orginal_sar_avg_var}

@@

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean. 
In the context of speckle filtering, table \ref{tbl:orginal_sar_avg_var} indicates the vicious circle: estimating variance is equal to estimating the mean and is equivalent to the main problem, ie. estimating the unknown parameter $\sigma$.

The formulas above has long been noted. In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al has noted the ratio of expected standard deviation to mean is a constant in both cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.

\subsection{ The effects of Heteroskedasticity on Speckle Filters }

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: 
Eventhough, the statistical model within individual resolution cell is well established, the applicability of its models is restricted to homogenous areas. 
Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.

@@

In this paper, we propose using base-2 logarithmic transformtion of SAR orignal random variables. Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet it maintains the ability to transform heterskedactic speckle into a homoskedastic relationship. Thus the original variables become:

@@

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as follows:

@@

Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$

@@

This result is consistence with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}.  
The main difference would be the use of base-2 logarithm which is prefered here for faster computation.

Table \ref{tbl:sar_variables_properties} summarize the discussion so far. 
It can be seen that while the original data, especially intensity values, should be prefered for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast. 
Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (inculding wavelets) and computational (including artificial neural network) techniques into SAR data.

@@

Noting the results from previous section, the pdf for these variable can be trivially given as

@@

From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider the random variable defined as the contrast between two measured samples, in the log-transformed domain:

@@

It could be seen that, in the log-transformed domain, not only the expected mean of observable variance is constant, the sampling distribution of this random variable is independent of $\sigma$. 
We have seen this analytically for two sample variances. 
For larger number of samples, Monte-Carlo simulation is used to visualise the PDF of sample variances.

In summary, a few measures of distance is shown to be consistent, which agrees with the consistent sense of variance / deviation and homoskedasticity.
The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use as illustrated in our kMLE speckle filter.
The consistent sense of contrast can be used to test if the any pair of measured data point belong to the same class of scatterrer, 
	and it may also explain why in original SAR domain the ratio based detector / classifier is prefered to the differential measures, which is not consistent. 
An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
The consistent sense of contrast also gives rise to the consistent measure of variance, which can be used to test if a group of pixel can form an homogenous area.
This is applied in a clustering algorithm described in \cite{Le_2010_ACRS}.

@@

Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and SAR speckle filtering process.
The ``SAR Processor'' block indicates either of the following processes.
First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded in $\tilde{X}$.
And second is the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
%In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
%Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.

@@

Logarithmic transformation offers several consistent measures of distance, 
	which is hypothised to be significant  in evaluating speckle filters.
	A case in point is in visual evaluation of filtered results on real captured SAR images.
Since the radiometric ground-truth is not available, %the most common 
%In real SAR captured images, the radiometric ground-truth normally is not available.
	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
Traditional method is to investigate the ratio images between the filtered output and the noisy input images.
Since logarithmic transformation convert these ratio into substractive residual
	, which are consistent, residual analysis can be used to analyse and evaluate the performance of speckle filters.
To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig. \ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is extremely subjective.

@@

\begin{subequations} \label{eqn:eval_metric}
\begin{align}
MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
\end{align}
\end{subequations}
%\begin{eqnarray}
%MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
%MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
%MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
%MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
%\end{eqnarray}

As qualititative visual evaluation is subjective by nature,
	quantitative metrics and measurements are preferred.
Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
When ground-truth is available, 
	either in simulated experiments or in homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated values and its true values.

>>>>

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
Estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance (hence lower MSE) indicating better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
Also, due to the stochastic nature of SAR processing, as well as simulating process, 
	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	prompting alternative evaluation criteria to be proposed.
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

The common theme is that each newly proposed speckle filter tends to be published along with a methodology for evaluating its performance.
Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
Some papers do present quantitative measurements, 
	however  due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The paper is structured as follows.
Section \ref{sec:lit_review} briefly surveys related work in the published literature, Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.

@@

%Addressing this issue, 
%There have been a few published articles dedicated to the topic of evaluating speckle filters.
%However, our survey of SAR speckle filtering research indicates 
%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
%In this section, we briefly review published work 
%	related to the topic of evaluating SAR speckle filters.	
It is customary to divide the performance evaluation of speckle filters across the two classes of 
	homogeneous and heterogeneous regions.
Across homogeneous areas,
	speckle filters are expected to estimate with negligible radiometric bias.
Thus evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
By contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is then to define a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.

Furthermore, its application in a SAR processing framework should allow an improvement in the measurement, detection or classification of the underlying radiometric features.
%As shown in the subsequent section, 
%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
The MSE evaluation is a combined evaluation of bias and variance error, and is therefore capable of evaluating the general requirement of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

For homogeneous scenes where the underlying radiometry is assumed to be constant, 
	the filtered results, statistically speaking, are considered to be samples of 
		a single but complex stochastic process.
%Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
	%are expected to estimate with no radiometry bias. 
%The best filters achieve maximum speckle suppression power in such areas.

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent index for evaluation would, of course, be a simple substraction.
In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.

@@

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the log-transformed domain.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters which is the primary criteria to evaluate speckle filters over homogeneous area.
%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
%	which is a component of MSE evaluation, 
%	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.

Real-life and practical images, however, are not homogeneous.
Thus there are a few associated difficulties in evaluating speckle filters over heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous
However, without simulation or access to solid ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise the noise being removed, (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluation, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
The ratio image then becomes a simple subtraction image.
The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).

@@

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional levels.
In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

@@

Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. 
Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

@@

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss Markov theorem becomes applicable again, 
	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
Initial intitution suggests that each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is presented and discussed, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

@@

SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components, each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. This interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.

@@

It is then trivial to prove that amplitude and intensity are simply scaled versions of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
These relationships evidently manifest a multiplicative nature. 
In fact, this condition has long been noted, but from different perspectives, in various SAR models including the multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. 
Consequently, the population expected mean and variance of the four distributions are given in Table \ref{tbl:orginal_sar_avg_var}.

@@

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean. 
In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; estimating variance is equal to estimating the mean and is equivalent to the main problem, ie. estimating the unknown parameter $\sigma$.

The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.

\subsection{The effects of Heteroskedasticity on Speckle Filters}

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: 
Even though the statistical model within individual resolution cells is well established, the applicability of its models is restricted to homogenous areas. 
Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and subsequently what to do in the case of heterogeneity.

@@

In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data. Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet maintains an ability to transform heterskedactic speckle into a homoskedastic relationship. Thus the original variables become:

@@

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variables as follows:

@@

Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$

@@

This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. The main difference would be the use of base-2 logarithm which is prefered here for faster computation.

Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
It can be seen that while the original data, especially intensity values, should be preferred for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast. 
Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (including wavelets) and computational (including artificial neural network) techniques into SAR data.

@@

Noting the results from the previous section, the pdf for these variable can be trivially given as

@@

From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider a random variable defined as the contrast between two measured samples, in the log-transformed domain:

@@

It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance constant but the sampling distribution of this random variable is independent of $\sigma$. 
We have seen this analytically for two sample variances. 
For a larger number of samples, Monte-Carlo simulation can be used to visualise the PDF of sample variances.

In summary, a few measures of distance are shown to be consistent, which agree with the consistent sense of variance / deviation and homoskedasticity.
The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use this way is illustrated in our kMLE speckle filter.
The consistent sense of contrast can be used to test if any pair of measured data points belong to the same class of scatterer. It may also 
explain why, in the original SAR domain, the ratio based detector / classifier is prefered to differential measures, which are not consistent. 
An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
The consistent sense of contrast also gives rise to a consistent measure of variance, which can be used to test if a group of pixels can form a homogenous area.
This is applied in a clustering algorithm described in \cite{Le_2010_ACRS}.

@@

Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and SAR speckle filtering process.
The ``SAR processor'' block indicates that either of the following processes is occuring.
First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded in $\tilde{X}$.
And second is the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
%In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
%Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.

@@

Logarithmic transformation offers several consistent measures of distance, 
	which is hypothised to be significant  in evaluating speckle filters.
	A case in point is in visual evaluation of filtered results on real captured SAR images.
Since the radiometric ground-truth is not available, %the most common 
%In real SAR captured images, the radiometric ground-truth normally is not available.
	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
A traditional method is to investigate the ratio images between the filtered output and the noisy input images.
Since logarithmic transformation convert these ratio into substractive residual
	, which are consistent, residual analysis can be used to analyse and evaluate the performance of speckle filters.
To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig. \ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is of course itself a subjective one.

@@

\begin{subequations} \label{eqn:eval_metric}
\begin{align}
MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
MSE_{noise} = MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
\end{align}
\end{subequations}
%\begin{eqnarray}
%MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
%MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
%MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
%MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
%\end{eqnarray}

As qualititative visual evaluation is subjective by nature,
	quantitative metrics and measurements are preferred, if relevant and possible.
Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
When ground-truth is available, 
	either in simulated experiments or over homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated and true values.

In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be estimated reasonably well.
Thus the base MSE level which is also a measure of the speckle noise level, can also be estimated.
Naturally, the speckle filter should remove as much noise as possible, 
	while it also should not remove more variations than that caused by the speckle noise.
%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base
